---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gbifliterature

<!-- badges: start -->
<!-- badges: end -->

The goal of gbifliterature is to connect with GBIF Literature API and retrive the full information by year.

## Installation

You can install the development version of gbifliterature from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("alrobles/gbifliterature")
```

## Example GBIF literature by year
We starting download all the literature from 2022. We use `get_gbif_literature_year` to get the literature for the specific 2022 year from the API.

```{r eval=FALSE} 
lit_2001 <- gbifliterature::get_gbif_literature_year(year = 2001)

```
You can print the output object if you want. The output is a data frame containing all the information related to GBIF peer reviewed literature in 2022

## Download all GBIF iterature
In the last example we observe that it's possible to map this function passing the year parameter:


```{r eval=FALSE}
library(purrr)
literature_df <- map_df(2000:2022, function(x){
    gbifliterature::get_gbif_literature_year(year = x)
  })
```

