---
title: "How to Retrive GBIF Literature"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to Retrive GBIF Literature}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
options(repos="https://cran.rstudio.com")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction
In this vignette we are going to download all GBIF literature available using
our `gbifliterature` R package.


The first step is install the package and also the `purrr` package to help us in download all literature.
```{r setup}
install.packages("purrr")
install.packages("remotes")
remotes::install_github("alrobles/gbifliterature")


```


# Example GBIF literature by year
We starting download all the literature from 2022. We use `get_gbif_literature_year` to get the literature for the specific 2022 year from the API.

```{r}
lit_2001 <- gbifliterature::get_gbif_literature_year(year = 2001)

```
You can print the output object if you want. The output is a data frame containing all the information related to GBIF peer reviewed literature in 2022

# Download all GBIF iterature
In the last example we observe that it's possible to map this function passing the year parameter:


```{r}

literature_df <- purrr::map_df(2000:2022, function(x){
    gbifliterature::get_gbif_literature_year(year = x)
  })```
